---
title: "nlmixr2qual Qualification Summary"
format:
  html:
    toc: true
    embed-resources: true
params:
  result_rds: ""
---

```{r}
#| echo: false
res <- readRDS(params$result_rds)
```

# Overall verdict

**`r if (isTRUE(res$overall)) "OVERALL: PASS" else "OVERALL: FAIL"`**

Only strict (deterministic-method) references gate this verdict; informational
(stochastic-method) references are reported below but never gate it.

# Summary

One row per reference: its own recorded objective function value (`ofv_ref`)
against this install's re-fit (`ofv_local`).

```{r}
#| echo: false
knitr::kable(res$summary, row.names = FALSE)
```

# Per-reference comparisons

Parameter estimates, precisions (standard errors), objective function value,
and shrinkage for each tested reference, comparing the stored reference value
against this install's local re-fit.

```{r}
#| echo: false
#| results: asis
for (id in names(res$details)) {
  row <- res$summary[res$summary$id == id, ]
  status <- if (isTRUE(row$pass[1])) "PASS" else "FAIL"
  kind <- if (isTRUE(row$strict[1])) "strict" else "informational"
  cat("\n## ", id, " — ", status, " (", kind, ")\n\n", sep = "")
  d <- res$details[[id]]
  names(d) <- c("Quantity", "Class", "Reference", "Local", "Rel. diff", "Tolerance", "Pass")
  print(knitr::kable(d, row.names = FALSE, digits = 6))
  cat("\n")
}
```

# Environment & provenance

```{r}
#| echo: false
str(res$provenance)
```
