---
title: "nlmixr2 Qualification Report"
format:
  html:
    toc: true
    embed-resources: true
params:
  bundle: ""
---

```{r setup, include=FALSE}
bundle <- readRDS(params$bundle)
knitr::opts_chunk$set(echo = FALSE)
```

# Executive summary

**Overall verdict: `r bundle$verdict$verdict`**

This is a *reproducibility* qualification: a PASS means this installation
reproduces the qualified single-threaded canonical reference within tolerance.
It does **not** assert scientific correctness or accuracy against a known truth.

Results are not guaranteed bit-identical across operating systems, CPU
architectures, compilers, or BLAS/LAPACK backends; tolerances absorb that noise
and the environment is recorded below for comparison against the baseline.

```{r}
p <- bundle$provenance
knitr::kable(data.frame(Field = names(unlist(p)), Value = unlist(p)))
```

# Environment & version gate

```{r}
knitr::kable(bundle$version_gate$detail)
```

# Per-model results

```{r results='asis'}
for (r in bundle$results) {
  cat("\n## ", r$model, " (", r$method, ") — ",
      if (r$pass) "PASS" else "FAIL", "\n\n", sep = "")
  print(knitr::kable(r$detail))
}
```

# Thread-invariance (multi-threaded re-fit vs single-threaded baseline)

```{r results='asis'}
if (is.null(bundle$invariance)) {
  cat("Not run.\n")
} else {
  for (r in bundle$invariance) {
    cat("\n## ", r$model, " @ ", r$threads, " threads — ",
        if (r$pass) "PASS" else "FAIL",
        if (isTRUE(r$informational)) " (informational)" else "", "\n\n", sep = "")
    print(knitr::kable(r$detail))
  }
}
```

# Appendix: session info

```{r}
sessionInfo()
```
